This section discusses
\begin {enumerate}
\item the requirements for the different channels through which the system can be accessed by
people and systems, and
\item the integration channels which must be supported by this system.
This section specifies the different channels through which users will be able to access the system
services.
\end{enumerate}
\subsubsection{Human Access Channels}
The system will be accessible by human users through the following channels:\par
\begin{itemize}
\item From a web browser through a rich web interface. The system must be accessible from any of the standards-compliant web browsers including all recent versions of Mozilla Firefox, Google Chrome, Apple Safari and Microsoft Internet Explorer.
\item From mobile devices if time allows it.
\end{itemize}
\subsubsection{System Access Channels}
\begin{itemize}
\item Other systems should be able to access services offered by STORM. Perhaps direct feed of teams into other systems.
\item Various technologies will be used such as:
	\begin{itemize}
	\item Node.js
	\item Express.js
	\item EJS
	\item Mongoose
	\item SMTP
	\end{itemize}
\end{itemize}
\subsubsection{Integration channels}
The system will allow manual integration through importing and exporting of CSV
files. In particular, the system will support
\begin{itemize}
\item Importing of subject data from CSV files.
\item Importing of new criteria for shuffling subjects from CSV files.
\item Exporting of groups to CSV files.
\item Exporting of subject data for offline editing to CSV files.
\end{itemize}


