\subsection{History and Background}
\subsubsection{A Brief History of Project STORM}
In 2013 lecturers of the department of Computer Science, which resides at the University of Pretoria,
approached honors students of the module “Educational Software Development” to develop a team
shuffling system. 
The system was going to be used by the lecturers of the module “Software Engineering” to
determine teams for the “Rocking the boat” exercise of the Software Engineering module using a
set of lecturer defined criteria to select the teams with. An incomplete requirements specification document
was designed and the project was brought to an end. 

\subsubsection{Project Background}
The lecturers of the "Software Engineering" module sought the need for such a shuffling tool, this
time approaching students of the "Software Development" module. The requirements specification previously 
developed will be used as a starting point. This document will be stripped down to a "basic system" requirements
specification, not completely discarding functionality specified in the previous documentation but adding relevant functionality
as the development life-cycle persists.

\subsection{Project Scope}
The complete system should enable users to build teams, from a list of students, by selecting a
set of criteria. This will aid the users in such a way that the users do not have to build the teams
manually, which may require a lot of time. The users can spend their time rather on analyzing
the results of each “Rocking the Boat” round to change the criteria for the next round more
effectively.
